---
title: "Robust Persistence Diagrams"
subtitle: "Using Reproducing Kernels"
author: "Siddharth Vishwanath"
date: "NeurIPS 2020"
output:
  md_document:
    variant: gfm

---


```{r setup, include=FALSE,echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source('./RKDE.R')
source('./ph-functions.R')
```

This page describes the method to construct robust persistence diagrams, as implemented in our paper [Robust Persistence Diagrams using Reproducing Kernels](https://arxiv.org/abs/2006.10012). 

You will need the following dependencies for implementing the analyses using R. Please run the following code:

``` r
pkgs <- c("dplyr","plotrix","spatstat","TDA","hitandrun","functional","Rfast","plotly","viridis","plot3D")
sapply(pkgs, install.packages, character.only=TRUE)
```

## Here’s an example for computing the persistence diagrams

We start by sampling points $\mathbb{X}_n$ from a circle in 2D with some uniform noise in the enclosing region. 


```{r}
set.seed(2020)
signal <- circleUnif(400,4)*rnorm(400,1,0.1)
noise <- matrix(runif(2*1000,-8,8),ncol=2)
X <- rbind(signal,noise)
plot(X,asp=1,pch='.')
draw.circle(0,0,4,border = alpha('red',0.1),lwd=3)
```

Here are the persistence diagrams. 

### 1. Distance Function Persistence Diagram
```{r message=FALSE, results='hide'}
dgm.distFct <- ph.distfun(X,by=0.1,H=0)$diagram
plot.diagram(dgm.distFct)
```


### 2. DTM Persistence Diagram
```{r message=FALSE, results='hide'}
dgm.dtm <- ph.dtm(X,by=0.1,m0 = M0(X,3))$diagram
plot.diagram(dgm.dtm)
```


### 3. KDE Persistence Diagram
```{r message=FALSE, results='hide', eval=FALSE}
dgm.kde <- ph.kde(X,by=0.1,H=bw(X,3))$diagram
plot.diagram(dgm.kde)
```

```{r echo=FALSE}
dgm.kde <- ph.kde(X,by=0.1,H=bw(X,3))$diagram
plot.diagram(dgm.kde, diagLim = c(0,0.04))
```



### 4. Robust Persistence Diagram
```{r message=FALSE, results='hide', eval=FALSE}
dgm.rkde <- ph.rkde2(X,by=0.1,H=bw(X,3))$diagram
plot.diagram(dgm.rkde)
```

```{r echo=FALSE}
dgm.rkde <- ph.rkde2(X,by=0.1,H=bw(X,3))$diagram
plot.diagram(dgm.rkde, diagLim = c(0,0.04))
```