---
title: "Experiment - I"
author: "Siddharth Vishwanath"
date: "17/10/2020"
output:
  md_document:
    variant: gfm
---

```{r include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(scales)
library(plot3D)
```

```{r results='hide', message=FALSE,echo=FALSE}
root <- "/Users/vishwanathgl/Documents/Github/robust-PDs"
knitr::opts_knit$set(root.dir = "/Users/vishwanathgl/Documents/Github/robust-PDs")
library(latex2exp)
```

```{r echo=FALSE, results='hide', message=FALSE}
source('./RKDE.R')
source('./ph-functions.R')
source('./Clustering/spectral-functions.R')

dims <- c(0,1,2)
load('./Clustering/data/X.RData')
load('./Clustering/data/cls.RData')
load('./Clustering/data/dist-dgms.RData')
load('./Clustering/data/rkde-dgms.RData')
ad <- lapply(dist.dgms,function(x)x$diagram)
rd <- lapply(rkde.dgms,function(x)x$diagram)
```

```{r echo=FALSE, results='hide', message=FALSE, cache=TRUE}
Delta.imgs <- pimg.dist.matrix(ad)
AD <- Delta.imgs[[1]]
AD1 <- Delta.imgs[[2]]
AD2 <- Delta.imgs[[3]]

A.Dist  <-  pmax(AD[[1]],AD[[2]],AD[[3]])
A1.Dist <- pmax(AD1[[1]],AD1[[2]],AD1[[3]])
A2.Dist <- pmax(AD2[[1]],AD2[[2]],AD2[[3]])
```

```{r echo=FALSE, results='hide', message=FALSE, cache=TRUE}
Delta.dgms <- dgm.dist.matrix(rd)
RD  <- Delta.dgms[[1]]
RD1 <- Delta.dgms[[2]]
RD2 <- Delta.dgms[[3]]

R.Dist  <-  pmax(RD[[1]],RD[[2]],RD[[3]])
R1.Dist <- pmax(RD1[[1]],RD1[[2]],RD1[[3]])
R2.Dist <- pmax(RD2[[1]],RD2[[2]],RD2[[3]])
```


## Spectral Clustering using Persitent Homology

Load the necessary data. `X.RData` contains 150 three-dimensional point clouds from 6 different classes. `cls.RData` contains the class information. The pre-trained persistence diagram from the distance function, and the robust persistence diagrams are stored in `dist-dgms.RData` and `rkde-dgms.RData`. 


```{r eval=FALSE, include=TRUE}
## Preliminaries
root <- "/path/to/root/directory/"
setwd(root)

source('./RKDE.R')
source('./ph-functions.R')
source('./Clustering/spectral-functions.R')

## Load the pre-trained Data
load('./Clustering/data/X.RData')         # Point clouds
load('./Clustering/data/cls.RData')       # Corresponding class
load('./Clustering/data/dist-dgms.RData') # Dgm from distance function
load('./Clustering/data/rkde-dgms.RData') # Robust persistence Dgm

ad <- lapply(dist.dgms,function(x)x$diagram)
rd <- lapply(rkde.dgms,function(x)x$diagram)



```

Some sample plots:
```{r results='hide'}
set.seed(1)
idx <- sample(1:25,6,replace = F) + seq(0,125,by=25)
par(mfrow=c(3,2),oma=c(2,2,2,2),mar=c(1,1,1,1))
sapply(idx,function(i){
    P <- X[[i]]
    scatter3D(P[,1],P[,2],P[,3],col=alpha("black",0.5), pch=20, main=cls[[i]],phi = 30, cex=0.3)
    return(T)})
```

Compute the distance matrices:
```{r eval=FALSE, include=TRUE}
Delta.imgs <- pimg.dist.matrix(ad)
Delta.dgms <- dgm.dist.matrix(rd)
```



Some sample images for the pairwise distance matrix:

(1). H0, Winf for Persistence Image
```{r}
Delta.dgms[[1]][[1]] %>% image(col=viridis(20,option = 'C'))
```

(2). H0, Winf for Persistence Image
```{r}
Delta.imgs[[1]][[1]] %>% image(col=viridis(20,option = 'C'))
```

The results from spectral clustering:
```{r message=FALSE, warning=FALSE}
numclasses <- c(1:6)
names(numclasses) <- c('noise','sphere','torus','circle','3clust','9clust')

n <- 100

set.seed(2020)
scc <- clust_rand_index(n,cls,numclasses,Delta.dgms, Delta.imgs)
scc$summary
```









